---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# phslookups

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

The goal of phslookups is to provide helper functions to easily access and use lookups which have been provided for analysis.

## Installation

If you are internal to PHS, you can install the latest version of phslookups from the internal Posit Package Manager.

``` r
# On the Posit Workbench
install.packages("phslookups")

# On RStudio Desktop it might be nessecary to specify the repository
install.packages("phslookups", repos = "https://ppm-prod.publichealthscotland.org/phs-github/latest")
```

To install the development version directly from GitHub.

``` r
remotes::install_github("Public-Health-Scotland/phslookups")
```

Note that phslookups will never be available on CRAN as it is intended to be an internal-only package, and relies on lookup files on internal-only drives.

## Available lookups

-   The Scottish Postcode Directory - `get_spd()`
-   HSCP Localities - `get_hscp_locality()`
-   SIMD lookups - `get_simd_datazone()` and `get_simd_postcode()`

## Example

Load the latest available version of the full Scottish Postcode Directory.

```{r spd_latest_full}
library(phslookups)

spd <- get_spd()
head(spd)
```

Get a specific version of a file, great if you want to 'lock' your code to a specific version too.

```{r version_examples}
library(phslookups)

spd_23 <- get_spd(version = "2023_2")
localities_mar_24 <- get_hscp_locality(version = "20240308")
simd_dz_2016 <- get_simd_datazone(simd_version = "2016")
simd_pc_2016_2012 <- get_simd_postcode(postcode_version = "2016_1", simd_version = "2012")
```

Select only the necessary columns to reduce memory use and improve speed.

```{r col_select_examples}
library(phslookups)
library(dplyr)

postcode_coords <- get_spd(col_select = c("pc7", "latitude", "longitude"))
locality_lookup <- get_hscp_locality(col_select = c("datazone2011", "hscp_locality"))

simd_dz_2016 <- get_simd_datazone(simd_version = "2016")

get_simd_datazone(
  simd_version = "2016",
  col_select = c("DataZone2011", contains("quintile"))
)
```
