---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# phslookups

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

The goal of phslookups is to provide helper functions to easily access and use lookups which have been provided for analysis.

## Installation

You can install the latest version of phslookups from [GitHub](https://github.com) with:

``` r
remotes::install_github("Public-Health-Scotland/phslookups")
```

It is not yet available from the PHS Posit Package Manager, it will never be available on CRAN as it is intended to be an internal only package.

## Example

Load the Scottish Postcode Directory

```{r example}
library(phslookups)

spd <- get_spd()
```
